High-Dimensional Regularized Discriminant Analysis

### 2017-10-15 reports/paper-hdrda.Rnw
use Taylor and Francis latex template #29

\documentclass[review,authoryear]{elsarticle}

\usepackage{graphicx, amsmath, amssymb, bm, mathtools, amsthm, natbib}
\usepackage{algorithm2e, url}

\bibpunct{(}{)}{;}{a}{,}{,}

@@

%----------------Page dimensions ----------------
\oddsidemargin 0.0in
\evensidemargin 0.0in
\topmargin -0.75in
\leftmargin 0in
\headheight 0.0in
\headsep 0.5in
\footskip 0.5in
\footnotesep 0.0in
\textwidth 6.5in
\textheight 9.5in

@@

\begin{frontmatter}

@@

\author[jar]{John A. Ramey\cortext[cor1]{Corresponding author}}
\author[cks]{Caleb K. Stein}
\author[pdy]{Phil D. Young}
\author[dmy]{Dean M. Young}
\address[jar]{Novi Labs}
\address[cks]{Myeloma Institute, University of Arkansas for Medical Sciences}
\address[pdy]{Department of Management and Information Systems, Baylor University}
\address[dmy]{Department of Statistical Science, Baylor University}

@@

\begin{keyword}
Regularized discriminant analysis\sep High-dimensional classification\sep Covariance-matrix regularization\sep Singular value decomposition\sep Multivariate analysis\sep Dimension reduction
\MSC[2010] 62H30\sep 65F15\sep 65F20\sep 65F22
\end{keyword}

\end{frontmatter}

>>>>

\documentclass[]{interact}

\usepackage{graphicx, mathtools, amssymb, bm, amsthm}
\usepackage{algorithm2e, url}

% Journal Specific

% natbib.sty for citation and bibliography support
\usepackage[numbers,sort&compress]{natbib}
\bibpunct[, ]{[}{]}{,}{n}{,}{,}
\renewcommand\bibfont{\fontsize{10}{12}\selectfont}
\makeatletter% @ becomes a letter
\def\NAT@def@citea{\def\@citea{\NAT@separator}}% Suppress spaces between citations using natbib.sty
\makeatother% @ becomes a symbol again

@@

@@

%\articletype{ARTICLE TEMPLATE} % Specify the article type or omit as appropriate

@@

% \author{
% \name{John.~A. Ramey\textsuperscript{a}\thanks{CONTACT John.~A. Ramey. Email: johnramey@gmail.com}, Caleb~K. Stein\textsuperscript{b}, Phil~D. Young\textsuperscript{c}, and Dean~M. Young\textsuperscript{d}}
% \affil{\textsuperscript{a}Novi Labs, Austin, TX, USA; \textsuperscript{b}Myeloma Institute, University of Arkansas for Medical Sciences, Little Rock, AR, USA; \textsuperscript{c}Department of Management and Information Systems, Baylor University, Waco, TX, USA; \textsuperscript{d}Department of Statistical Science, Baylor University, Waco, TX, USA;}
%}

\author{
\name{A.~N. Author\textsuperscript{a}\thanks{CONTACT A.~N. Author. Email: latex.helpdesk@tandf.co.uk} and John Smith\textsuperscript{b}}
\affil{\textsuperscript{a}Taylor \& Francis, 4 Park Square, Milton Park, Abingdon, UK; \textsuperscript{b}Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t, Freiburg, Germany}
}

@@

% TODO: Are these codes needed?
% \MSC[2010] 62H30\sep 65F15\sep 65F20\sep 65F22
\begin{keywords}
Regularized discriminant analysis; High-dimensional classification; Covariance-matrix regularization; Singular value decomposition; Multivariate analysis; Dimension reduction
\end{keywords}
